### 2011-02-10 paper/futureWork.tex
Added paperOutline
lots of editing of the intro/motivation/previouswork, and some in the robot platform
Minor
More fitness, explanation of bias due to sensor area
Conclusion/Future Work

%\section{Future work}

\edit{write this, old section below}

% What are the major shortcomings of your current method? For each 
% shortcoming, propose additions or enhancements that would help overcome it.

There are several directions in which we could continue our
work. First, the error margins for our runs were large, so reducing
them by running more trials would lead to more conclusive data. It
would also be insightful to run our algorithms on different motion
models.  We suspect that our choice of motion model influenced the
results greatly, as even random choices in the space produced gaits
that moved a significant fraction of the time (> 5\%).  It would be
interesting to see how learning methods would perform using a model
that included a much higher percentage of unproductive gaits. We also
intend to experiment further with SVM regression and evolutionary
algorithms/HyperNEAT.  Some parameter vectors resulted in the robot
turning, as opposed to it walking long distances. This could be an
interesting learning goal in future projects. To these ends, we
propose the following additions and enhancements:

\begin{itemize}
\item More runs and/or longer runs
\item Different motion representations
\item Better tuning of SVM regression
\item Evolutionary algorithms/HyperNEAT\cite{clune}
\item Learning how to turn
\end{itemize}

>>>>

%\section{Future work}
\seclabel{futureWork}

Because all trials were done in hardware, it was difficult to gather
the thousands of trials that would be necessary to establish a more
rigorous statistical ranking of the methods' performance, or their
asymptotic behavior as longer and longer training runs are allowed.
Thus, one extension of the current work would be to obtain these
thousands more trials.

However, a more effective extension might be to combine trials in
simulation and in hardware, perhaps doing only every tenth or
hundredth trial in hardware.  The simulation would produce the
necessary volume of trials to allow the learning methods to be
effective, and the hardware trials would serve to continuously ground
and refine the simulator.  One could also guide evolution to the most
fertile territory by penalizing gaits that produced large
discrepancies between simulation and reality.

Another natural extension would be to allow gaits with feedback;
i.e. gaits that depend not only on time, but also the measured
position of the legs, voltage drop across the servos, etc.
